### 2015-02-27 paper_10_intro.tex
switched references to biblatex
completed Indicators, working on balanced scorecard
change name to CRI

    Software development organizations need a framework to define
    what measurements should be tracked and how those measurements
    should be reported.  The MPI framework provides a solid foundation
    for a consistent evaluation.  MPI analyzes the historical performance
    of an SDO
    to create a baseline in order to provide a broad
    view of the overall organization.  It is common for software development
    organizations to measure and focus soley on the source code
    being produced.  However, a software development organization does more
    than just produce source code.  There is documentation to be
    written, testcases to be created, systems to be deployed, and
    decisions to be made.  The framework provides an evaluation
    of the overall software development organization, not just the
    source code.

@@

    Another promising research area is \textit{process mining}.
    As stated by Wil van der Aalst \cite{vanderAalst2011}, 
    ``The idea of process mining is to discover, monitor
    and improve real
    processes (i.e., not assumed processes) by extracting knowledge from event logs
    readily available in today's systems.''  Creating software involves
    a vast amount of processes.  Numerous logs of raw data are collected.  
    One application of process mining in the area of software development
    was an algorithm and information for measuring a software engineering process from
    the Software Configuration Management (SCM) \cite{Rubin2007}.
    The technique creates process models 
    to understand the process of developing software and code. 
    It is less focused on the output and results,
    but it is more focused on adherence to a specified process.

@@

The remainder of this dissertation is divided into 5 chapters.  The next chapter provides
an overview of software, software development lifecycles, software engineering, and software
development organizations.  Chapter 3 introduces what is meant by the term data-driven
software engineering. Chapter 4 then provides an explanation of the Master Performance 
Indicator (MPI).  It will present the essential elements for calculating the MPI, as well
as the formulas, framework, and data necessary to produce the MPI. Chapter 5 provides
a technological framework for generating and storing the current and historical MPI values.
Chapter 6 demostrates how MPI can be implemented in a software development portion of 
a large financial institution.  Chapter 7 concludes the dissertation with a summary
of the results and some possible future directions for further enhancements.

>>>>

    Software development organizations need a framework to define
    what measurements should be tracked and how those measurements
    should be reported.  The Cumulative Result Indicator (CRI)
    framework provides a solid foundation
    for a consistent evaluation.  CRI analyzes the historical performance
    of an SDO
    to create a baseline in order to provide a broad
    view of the overall organization.  It is common for software development
    organizations to measure and focus soley on the source code
    being produced.  However, a software development organization does more
    than just produce source code.  There is documentation to be
    written, testcases to be created, systems to be deployed, and
    decisions to be made.  The framework provides an evaluation
    of the overall software development organization, not just the
    source code.

@@

    Another promising research area is \textit{process mining}
    \cite{vanderAalst2012}.
    As stated by Wil van der Aalst \cite{vanderAalst2011}, 
    ``The idea of process mining is to discover, monitor
    and improve real
    processes (i.e., not assumed processes) by extracting knowledge from event logs
    readily available in today's systems.''  Creating software involves
    a vast amount of processes.  Numerous logs of raw data are collected.  
    One application of process mining in the area of software development
    was an algorithm and information for measuring a software engineering process from
    the Software Configuration Management (SCM) \cite{Rubin2007}.
    The technique creates process models 
    to understand the process of developing software and code. 
    It is less focused on the output and results,
    but it is more focused on adherence to a specified process.

@@

    The remainder of this dissertation is divided into 5 chapters.  The next chapter provides
    an overview of software, software development lifecycles, software engineering, and software
    development organizations.  Chapter 3 introduces what is meant by the term data-driven
    software engineering. Chapter 4 then provides an explanation of the Cumulative
    Result Indicator (CRI).  It will present the essential elements for calculating the CRI, as well
    as the formulas, framework, and data necessary to produce the CRI. Chapter 5 provides
    a technological framework for generating and storing the current and historical CRI values.
    Chapter 6 demostrates how CRI can be implemented in a software development portion of 
    a large financial institution.  Chapter 7 concludes the dissertation with a summary
    of the results and some possible future directions for further enhancements.

### 2015-02-27 paper_30_measure.tex
adding data files
change name to CRI

    This work will focus on steps 1 and 2.  The process issue is the overall
    effectiveness of the SDO.  Section \ref{sec:MPI} will cover step 2 as
    it relates to an SDO.  Step
    3 will be different for each SDO, but Section \ref{sec:SDLC-AE} provides
    a bit of guidance for storing the correct information.  It is up to the
    specific SDO to determine how and when the information is being stored.

@@

        How can the PIs, RIs, KRIs, and KPIs be combined to form a single
        value called an MPI (Master Performance Indicator)?  If the indicators
        are targeted for upper management to understand performance, then 
        KPIs are not the correct indicators.  KPIs are targeted towards
        immediate action and future performance.  RIs and KRIs are the most
        beneficial for upper management to gauge how an organization is doing.
        However, with so many possible RIs and even KRIs, it can be tricky
        to gain a quick understanding.  The next section will present
        and explain a technique to combine KRIs into a single number
        for immediate and  effortless evaluation of an SDO.

>>>>

    This work will focus on steps 1 and 2.  The process issue is the overall
    effectiveness of the SDO.  Section \ref{sec:CRI} will cover step 2 as
    it relates to an SDO.  Step
    3 will be different for each SDO, but Section \ref{sec:SDLC-AE} provides
    a bit of guidance for storing the correct information.  It is up to the
    specific SDO to determine how and when the information is being stored.

@@

        How can the PIs, RIs, KRIs, and KPIs be combined to form a single
        value called the CRI (Cumulative Result Indicator)?  If the indicators
        are targeted for upper management to understand performance, then 
        KPIs are not the correct indicators.  KPIs are targeted towards
        immediate action and future performance.  RIs and KRIs are the most
        beneficial for upper management to gauge how an organization is doing.
        However, with so many possible RIs and even KRIs, it can be tricky
        to gain a quick understanding.  The next section will present
        and explain a technique to combine KRIs into a single number
        for immediate and  effortless evaluation of an SDO.

### 2015-02-27 paper_50_sdlc-ae.tex
chapter 3 work
mostly done with chapter 3
change name to CRI

% All about the SDLC Analytic Engine
\section{SDLC ANALYTIC ENGINE}

In order for an SDO to properly track the elements of MPI, a data storage system should be available to store the appropriate data.  A consistent storage system should help to avoid the problem of inaccurate
data caused by numerous manipulations of the existing data \cite{Olson2003}. Plus, if the system
is implemented correctly by allowing limited changes to existing data, it will be able to alliviate
some of the dishonesty that is currently present in software projects \cite{Rost2011}. This storage system will be named the SDLC Analytic Engine (SDLC-AE). Figure \ref{fig:sdlc-ae} provides an overview of the data that could potentially be stored in the SDLC-AE.

@@

\subsection{DATABASE STRUCTURE}
   All the data necessary to compute MPI needs to be stored in a database.  This section will 
   lay out the structure of tables and relationships necessary to the store all the data
   within a relational database.

   \subsubsection{TABLES FOR RAW MPI DATA}

        The first set of tables that need to be created are tables
        to store the raw data that is collected.  These tables
        will line up with the necessary data for each of the 5 elements
        of MPI.  Figure \ref{fig:raw} provides a visual description
        of the tables that are needed.  The tables have no relationship
        with each other since they are raw data.  The primary goal of
        these tables is to store the raw data in a single database. The
        5 table names are:
        \begin{enumerate}
            \item QUALITY\_RAW
            \item AVAILABILITY\_RAW
            \item SATISFACTION\_RAW
            \item SCHEDULE\_RAW
            \item REQUIREMENTS\_RAW
        \end{enumerate}
        Notice these table names match with the 5 elements of MPI.

       \begin{figure}[ht]
            \centering
            \includegraphics[scale=.55]{images/raw_tables.png}
            \caption{TABLES FOR RAW MPI DATA}
            \label{fig:raw}
        \end{figure}%

        Appendix \ref{src:rawSQL} provides the necessary SQL statements to create the 
        database tables for storing the raw MPI data.  The SQL is written for an Oracle
        database, but the scripts can be modified to work with another database
        such as: PostgreSQL, SQL Server, or MySQL.

    \subsubsection{INTERMEDIATE SCORE TABLES FOR MPI}

        Appendix \ref{src:scoreSQL} provides the necessary SQL statements to create the 
        database tables for storing the intermediate MPI scores.

    \subsubsection{FINAL SCORE TABLES FOR MPI}

        Appendix \ref{src:overallscoreSQL} provides the necessary SQL statements to create the 
        database tables for storing the final scores for each element and the final 
        overall MPI scores for each time frequency.

\subsection{QUERIES}
    The section will provide the necessary SQL queries to obtain the correct data
    needed to compute the individual elements of MPI.

\subsection{COMPUTATIONS}
    This section will provide R scripts to calculate each individual score and the overall 
    MPI score. The scripts will need to be run every time the data is updated and the MPI
    score needs to be recalculated.

>>>>

% All about the SDLC Analytic Engine
\section{SDLC ANALYTIC ENGINE}
\label{sec:SDLC-AE}

In order for an SDO to properly track the elements of CRI, a data storage system should be available to store the appropriate data.  A consistent storage system should help to avoid the problem of inaccurate
data caused by numerous manipulations of the existing data \cite{Olson2003}. Plus, if the system
is implemented correctly by allowing limited changes to existing data, it will be able to alliviate
some of the dishonesty that is currently present in software projects \cite{Rost2011}. This storage system will be named the SDLC Analytic Engine (SDLC-AE). Figure \ref{fig:sdlc-ae} provides an overview of the data that could potentially be stored in the SDLC-AE.

@@

\subsection{DATABASE STRUCTURE}
   All the data necessary to compute CRI needs to be stored in a database.  This section will 
   lay out the structure of tables and relationships necessary to the store all the data
   within a relational database.

   \subsubsection{TABLES FOR RAW CRI DATA}

        The first set of tables that need to be created are tables
        to store the raw data that is collected.  These tables
        will line up with the necessary data for each of the 5 elements
        of CRI.  Figure \ref{fig:raw} provides a visual description
        of the tables that are needed.  The tables have no relationship
        with each other since they are raw data.  The primary goal of
        these tables is to store the raw data in a single database. The
        5 table names are:
        \begin{enumerate}
            \item QUALITY\_RAW
            \item AVAILABILITY\_RAW
            \item SATISFACTION\_RAW
            \item SCHEDULE\_RAW
            \item REQUIREMENTS\_RAW
        \end{enumerate}
        Notice these table names match with the 5 elements of CRI.

       \begin{figure}[ht]
            \centering
            \includegraphics[scale=.55]{images/raw_tables.png}
            \caption{TABLES FOR RAW CRI DATA}
            \label{fig:raw}
        \end{figure}%

        Appendix \ref{src:rawSQL} provides the necessary SQL statements to create the 
        database tables for storing the raw CRI data.  The SQL is written for an Oracle
        database, but the scripts can be modified to work with another database
        such as: PostgreSQL, SQL Server, or MySQL.

    \subsubsection{INTERMEDIATE SCORE TABLES FOR CRI}

        Appendix \ref{src:scoreSQL} provides the necessary SQL statements to create the 
        database tables for storing the intermediate CRI scores.

    \subsubsection{FINAL SCORE TABLES FOR CRI}

        Appendix \ref{src:overallscoreSQL} provides the necessary SQL statements to create the 
        database tables for storing the final scores for each element and the final 
        overall CRI scores for each time frequency.

\subsection{QUERIES}
    The section will provide the necessary SQL queries to obtain the correct data
    needed to compute the individual elements of CRI.

\subsection{COMPUTATIONS}
    This section will provide R scripts to calculate each individual score and the overall 
    CRI score. The scripts will need to be run every time the data is updated and the CRI
    score needs to be recalculated.

making decisions based upon historical data. 
Data Driven Software Engineering not Data Driven Software Development

### 2015-02-27 paper_60_tooling.tex
adding info about 3 focus areas and 3 questions
change name to CRI

\subsection{SDLC DASHBOARD}
This maybe needs a name: Project MPI????  The goal of this project is to provide a tool that
given the 5 files will be able to provide a score for the software department.  It should run 
as a web application.

This section will provide information to install and run a tool for calculating MPI for an organization.
\subsubsection{INTRODUCTION}
\subsubsection{OVERVIEW}
\subsubsection{INSTALLATION}
\subsubsection{DATABASE}
maybe MongoDB, maybe PostgreSQL/MySQL
\subsubsection{WEBSERVER}
The software can either run standalone on cloud-hosted platform such as Heroku.  Try using Play Framework 2 with Authenticate.

>>>>

% section not used in final dissertation

### 2015-02-27 paper_70_case-study.tex
change name to CRI

Data has been collected from the software development processes of
an SDO within a large financial institution.
The data collection was from 2007 to January 2015. As would be expected
in any organization, not all 5 elements have data for the entire duration.
MPI can still work because the calculations will only include
the available elements.  This section will provide the analysis performed and the MPI scores of that data.  An example of the initial analysis is included in \cref{app:case}.

\subsection{WITH HISTORICAL DATA}
    This first case will demonstrate how to calculate the MPI for an
    organization when historical data is present.  
    \subsubsection{QUALITY}
        Luckily, the data for quality goes from October 2007 to January 2015
        and contains 985 observations.
        This is important because historical data can be used to create the
        baseline quality function.  All quality for the years 2007 through 2013
        will be used as historical data for the purposes of creating
        the baseline quality function.  
    \subsubsection{AVAILABILITY}
    \subsubsection{SATISFACTION}
    \subsubsection{SCHEDULE}
    \subsubsection{REQUIREMENTS}
    \subsubsection{OVERALL}
        All of the months do not include the same elements.

An MPI calculation analyzing historical performance.

@@

%%An MPI calculation with default values for quality, schedule and requirements.

>>>>

Data has been collected from the software development processes of
an SDO within a large financial institution.
The data collection was from 2007 to January 2015. As would be expected
in any organization, not all 5 elements have data for the entire duration.
CRI can still work because the calculations will only include
the available elements.  This section will provide the analysis performed and the CRI scores of that data.  An example of the initial analysis is included in \cref{app:case}.

\subsection{WITH HISTORICAL DATA}
    This first case will demonstrate how to calculate the CRI for an
    organization when historical data is present.  
    \subsubsection{QUALITY}
        Luckily, the data for quality goes from October 2007 to January 2015
        and contains 985 observations.
        This is important because historical data can be used to create the
        baseline quality function.  All quality for the years 2007 through 2013
        will be used as historical data for the purposes of creating
        the baseline quality function.  
    \subsubsection{AVAILABILITY}
    \subsubsection{SATISFACTION}
    \subsubsection{SCHEDULE}
    \subsubsection{REQUIREMENTS}
    \subsubsection{OVERALL}
        All of the months do not include the same elements.

An CRI calculation analyzing historical performance.

@@

%%An CRI calculation with default values for quality, schedule and requirements.

### 2015-02-27 paper_80_conclusion.tex
change name to CRI

Due to the number of issues with surveys.  One area of future work would be indentifying
a general set of questions that would best fit MPI.  This set would have to include
the best number of questions, order of questions and wording of questions.  Therefore,
any new organization would not have to determine their own survey, but rather just use the
predetermined set of questions.  It would even be advantageous to build a software system to
handle the survey distribution and collection.  Ideally, the results would automatically be
inserted into the appropriate database tables for MPI scoring.

As shown in Table \ref{tab:bsc}, MPI is currently not addressing 2 characteristics of the balanced scorecard.  If the SDO does not operate on a fixed budget, MPI could be 
expanded to include another element for financial data. The challenge arises when
determining how to relate the SDO performance to finances.  The most likely scenario
would be a method to either select or predicted the expected software sales
for a month.  Then every month create an MPI element score that reflects
how much the expected sales were exceeded or missed.  The other missing
balanced scorecard characteristic is learning and growth.  Those are very difficult
to quantitatively measure.  In this case some possible data points might be:
hours of training, number of training courses, number of employees receiving
training, number of promotions, or another measure centered around training
courses and career growth.  Again, once data exists, the problem becomes finding
a baseline and measuring with respect to that baseline.

@@

There are many metrics that can be used to evaluate a Software Development Organization (SDO). 
Knowing which metrics to use and what they all mean can be a daunting task.  MPI is a
proposed solution to the difficulty of measuring an SDO.

Upon completion, this work shall identify:
\begin{itemize}
    \item Define \textbf{What} characteristics should be measured for an SDO
    \item Define \textbf{How} to measure those characteristics
    \item Map the relationship or lack of relationship with a Balanced Scorecard
    \item Create a Framework to store the necessary data for MPI
    \item Outline a Process to generate the MPI score
    \item Provide an example MPI score with real data
\end{itemize}

>>>>

Due to the number of issues with surveys.  One area of future work would be indentifying
a general set of questions that would best fit CRI.  This set would have to include
the best number of questions, order of questions and wording of questions.  Therefore,
any new organization would not have to determine their own survey, but rather just use the
predetermined set of questions.  It would even be advantageous to build a software system to
handle the survey distribution and collection.  Ideally, the results would automatically be
inserted into the appropriate database tables for CRI scoring.

As shown in Table \ref{tab:bsc}, CRI is currently not addressing 2 characteristics of the balanced scorecard.  If the SDO does not operate on a fixed budget, CRI could be 
expanded to include another element for financial data. The challenge arises when
determining how to relate the SDO performance to finances.  The most likely scenario
would be a method to either select or predicted the expected software sales
for a month.  Then every month create an CRI element score that reflects
how much the expected sales were exceeded or missed.  The other missing
balanced scorecard characteristic is learning and growth.  Those are very difficult
to quantitatively measure.  In this case some possible data points might be:
hours of training, number of training courses, number of employees receiving
training, number of promotions, or another measure centered around training
courses and career growth.  Again, once data exists, the problem becomes finding
a baseline and measuring with respect to that baseline.

@@

There are many metrics that can be used to evaluate a Software Development Organization (SDO). 
Knowing which metrics to use and what they all mean can be a daunting task.  CRI is a
proposed solution to the difficulty of measuring an SDO.

Upon completion, this work shall identify:
\begin{itemize}
    \item Define \textbf{What} characteristics should be measured for an SDO
    \item Define \textbf{How} to measure those characteristics
    \item Map the relationship or lack of relationship with a Balanced Scorecard
    \item Create a Framework to store the necessary data for CRI
    \item Outline a Process to generate the CRI score
    \item Provide an example CRI score with real data
\end{itemize}
